### 2018-11-02 introduction.tex
color-code commenting enabled

\section{Introduction}

Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}. In fact it is NP-hard in general to determine if there is a feasible solution to an MILP problem \cite{GJ79}. However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems. Modeling combinatorial optimization problems with MILPs also started the very popular area of LP-based approximation algorithms.

>>>>

\section{Introduction}
Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}. In fact it is NP-hard in general to determine if there is a feasible solution to an MILP problem \cite{GJ79}. However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems. Modeling combinatorial optimization problems with MILPs also started the very popular area of LP-based approximation algorithms.
